A weakly structured stem for human origins in Africa

### 2022-03-11 paper.tex
clean up figure and caption

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/proposed-models.png}
    \caption{
        \textbf{Proposed models of early human history in Africa.}
        seeking to reconcile genetic and paleoanthropological evidence \citep{Henn2018-rf}.
        \aprcomment{needs a caption}
    }
    \label{fig:proposed-models}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/proposed-models.png}
    \caption{
        \textbf{Proposed conceptual models of early human history in Africa.}
        These models have been designed to translate models from the 
        paleoanthropological literature into genetically testable demographic
        models \citep{Henn2018-rf}.
        We used these conceptual models as starting points to build detailed
        parameterized demographic models (Supp. Information section~\ref{modelspec})
        that were then fit to genetic data. 
    }
    \label{fig:proposed-models}
\end{figure}
